\bf\mftitle

### 2011-03-01 doc/jInfer/xsdimport/xsdimport.tex
"figure"

None of the modules provide nor require any tokens. Complete dependency tree is described in \cite[section 4]{archdoc} and depicted in Figure 9 of that document.

@@

For example, the \emph{attribute} tag can have a tag attribute \emph{use}.
While former will match \code{XSDTag.ATTRIBUTE}, the latter will match \code{XSDAttribute.USE}.
Lastly, tag attributes should not be confused with instances of \code{Attribute}, which is a class for storing information about the tag attributes inside jInfer. Every \code{Element} has a list of \code{Attribute}s, as can be seen from Figure 4 in \cite[section 2.3]{archdoc}.

@@

Diagram showing the inheritance of this interface, as well as both parsers bundled with jInfer, which implement it is in Figure \ref{parser_interface}.

>>>>

None of the modules provide nor require any tokens. Complete dependency tree is described in \cite[section 4]{archdoc} and depicted in figure 9 of that document.

@@

For example, the \emph{attribute} tag can have a tag attribute \emph{use}.
While former will match \code{XSDTag.ATTRIBUTE}, the latter will match \code{XSDAttribute.USE}.
Lastly, tag attributes should not be confused with instances of \code{Attribute}, which is a class for storing information about the tag attributes inside jInfer. Every \code{Element} has a list of \code{Attribute}s, as can be seen from figure 4 in \cite[section 2.3]{archdoc}.

@@

Diagram showing the inheritance of this interface, as well as both parsers bundled with jInfer, which implement it is in figure \ref{parser_interface}.
